Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
Fix section title
paper: handle overfull hboxes

\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries, with runtimes ranging from \runtimetreelowzero{} to \runtimetreehighzero{}, are an
order-of-magnitude faster than the baseline, with runtimes ranging from
\runtimetreelowbase{} to \runtimetreehighbase{}. We get another order-of-magnitude speedup when
optimizing for performance, achieving runtimes as low as \runtimetreelowone{} to
\runtimetreehighone{}. These speedups, ranging widely from \lowxalphazero{}x to 
\highxalphaone{}x, depending on $\alpha$ and query, constitute significant workflow improvements
for the analyst.

@@

\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the reference chained-equation decision trees model.
This measures the error introduced by on-the-fly imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time in the first place for dirty input data, for which ground truth is unavailable.

@@

\textbf{Planning Times}\quad
Planning times for our benchmark queries are reasonable, with mean planning times across the
benchmark queries ranging from \planningtimelow{} to \planningtimehigh{}, and ranging from
\planningtimelowpct{} to \planningtimehighpct{}\% of total runtime. In 99\% of individual
cases, the optimizer returned a query plan within \planningtimepninetynine{}. The choice of
$\alpha$ has no impact on planning times, because query selection is done after collecting
the Pareto frontier.

>>>>

\begin{sloppypar}
\textbf{Runtime vs. Base-table Imputation}\quad \Cref{fig:runtimes} summarizes the performance results. The quality-optimized
queries, with runtimes ranging from \runtimetreelowzero{} to \runtimetreehighzero{}, are an
order-of-magnitude faster than the baseline, with runtimes ranging from
\runtimetreelowbase{} to \runtimetreehighbase{}. We get another order-of-magnitude speedup when
optimizing for performance, achieving runtimes as low as \runtimetreelowone{} to
\runtimetreehighone{}. These speedups, ranging from \lowxalphazero{}x to 
\highxalphaone{}x, depending on $\alpha$ and query, constitute significant workflow improvements
for the analyst.
\end{sloppypar}

@@

\begin{sloppypar}
\textbf{Accuracy vs. Base-table Imputation (AVG)}\quad \Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results compared to the baseline, using the chained-equation decision trees model.
This measures the error introduced by on-the-fly imputation as compared to full imputation on the base tables.
This comparison is the relevant one in practice --- an analyst would only be considering the trade-offs in imputation quality and time for dirty input data when the ground truth is unavailable.
\end{sloppypar}

@@

\begin{sloppypar}
\textbf{Planning Times}\quad
Planning times for our benchmark queries are reasonable, with mean planning times across the
benchmark queries ranging from \planningtimelow{} to \planningtimehigh{}, and ranging from
\planningtimelowpct{} to \planningtimehighpct{}\% of total runtime. In 99\% of individual
cases, the optimizer returned a query plan within \planningtimepninetynine{}. The choice of
$\alpha$ has no impact on planning times, because query selection is performed after collecting
the Pareto frontier.
\end{sloppypar}
